Final Project Draft #2

### 2022-04-26 draft2.Rmd
original commit

---
title: 'Final Project Draft (enter actual title later)'
author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

@@

  theme_foundation() +
  theme(legend.title=element_blank())+
  theme(legend.background = element_blank())

>>>>

---
title: 'Final Project Draft #2'
author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

@@

  theme_foundation() +
  theme(legend.title=element_blank())+
  theme(legend.background = element_blank())
```
